---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tillsfunctionpackage

<!-- badges: start -->
<!-- badges: end -->

TODO: Describe what the package does... How to write readme: https://monashbioinformaticsplatform.github.io/2017-11-16-open-science-training/topics/rmarkdown.html

<!-- Start of my description -->
A collection of methods to estimate parameters of different tempered stable
distributions. Currently, there are three different tempered stable 
distributions to choose from: Tempered stable subordinator distribution, 
classical tempered stable distribution, normal tempered stable distribution.
The package also provides functions to compute characteristic functions and
tools to run Monte Carlo simulations.

The main function of this package are briefly described below:

*   main function: TemperedEstim() computes all the information about the
estimator. It allows the user to choose the preferred method and several
related options.
*   Characteristic function, density function, probability function and other 
functions for every tempered stable distribution mentioned above. 
E.g. charSTS(), dCTS(), ...
*   Monte Carlo simulation: a tool to run a Monte Carlo simulation (TemperedEstim_Simulation()) is provided and can save output files or 
produce statistical summary.

The package was developed by Till Massing and Cedric Jüssen and is structurally based on the "StableEstim" package by Tarak Kharrat and Georgi N. Boshnakov.

<!-- End of my description -->


## Installation

You can install the development version of tillsfunctionpackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cedricjuessen/tillsfunctionpackage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tillsfunctionpackage)
## basic example code
```

